Working title: Ecological network control

### 2018-05-03 paper/manuscript.Rmd
Finish maximum matching explanation

Strictly speaking, a matching in an unweighted directed graph is defined as a set of links that do not share a common start or end nodes, a node is matched if its at the end of a matched link and unmatched if not, and the largest possible matching is called maximum  matching. 
Maximum matching is a widely studied topic in graph theory and has been used in multiple real life applications, from dating apps and wireless communications to transplant donations and peer to peer file sharing.
Although seemingly unrelated, maximum matching is also connected to the controllability of a network because, as recently shown [@liu_controllability_2011], a matching can be decomposed into a set of paths that reveal how the control signal flows across the links in a network to reach every node that compose it. 
Unmatched nodes are the beginning of 
The result is that the minimum driver node set corresponds exactly to the *unmatched* nodes, those that which the control signal

to can be decomposed into a set of paths

A maximum matching is this. 
And can be calculatid this way. 
And gives this information. 
But its not unique.
This can provide extra information. 
Therefore we calculate them all.

>>>>

Maximum matching is a widely studied topic in graph theory and is commonly used in multiple applications, from dating apps and wireless communications to organ transplant allocation and peer to peer file sharing. 
A matching in an unweighted directed graph is as a set of links that do not share a common start or end nodes. 
A node is said to be superior if it is at the beginning of a matched link and called matched if it is at the end. 
Finally, the largest possible matching is called maximum matching. 
These definitions, however offer little insight about how maximum matching is related to structural controllability. 
The key is to note that these definitions imply that a matched node can have only one matched link pointing to it, and similarly a superior node can have at most one link leaving from it. 
The result is that a matching can actually be decomposed into a set of paths that reveal how a control signal can flow across the links in a network to reach every node that compose it. 
And so, as recently shown [@liu_controllability_2011], the minimum driver node set corresponds exactly to the *unmatched* nodes, those that are not controlled by other nodes in the network. 
The algorithm we use to find a maximum matching in a network is fully detailed in the Supplementary Information Section XX.
